---
title: "Loading Data"
author: "Ben Denis Shaffer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Loading Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Functions for Loading Data

The there five data loading functions, four for separate datasets needed to execute the analysis, and one that wraps around all four to load all data in one step:

* Load_Data
* Load_ModelData
* Load_FMIData
* Load_MSRPData
* Load_SpendData

# Model Data

Model Data consists of two datasets that are saved in an excel file. This file has two sheets/tabs, one with data variables aggregated to monthly level, and another with weekly level.

```{r, error=TRUE,  eval=FALSE}
mod_obj <- Load_ModelData(mod_obj, input_file_ModelData)
```

* Element added to `mod_obj` : `input_data` (List of two: `monthly`, `weekly`)
* Access via: `mod_obj$input_data` (List)
* Access via: `mod_obj$input_data$weekly` (data.frame)
* Access via: `mod_obj$input_data$monthly` (data.frame)

# FMI Data

Model Data consists of two datasets that are saved in an excel file. This file has two sheets/tabs, one with data variables aggregated to monthly level, and another with weekly level.

```{r, error=TRUE,  eval=FALSE}
mod_obj <- Load_ModelData(mod_obj, input_file_FMIData)
```

* Element added to `mod_obj` : `Ftable` 
* Access via: `mod_obj$Ftable` (data.frame)

# MSRP Data

Model Data consists of two datasets that are saved in an excel file. This file has two sheets/tabs, one with data variables aggregated to monthly level, and another with weekly level.

```{r, error=TRUE,  eval=FALSE}
mod_obj <- Load_ModelData(mod_obj, input_file_MSRPData)
```

* Element added to `mod_obj` : `Mtable` 
* Access via: `mod_obj$Mtable` (data.frame)

# Spend Data

Model Data consists of two datasets that are saved in an excel file. This file has two sheets/tabs, one with data variables aggregated to monthly level, and another with weekly level.

```{r, error=TRUE,  eval=FALSE}
mod_obj <- Load_ModelData(mod_obj, input_file_SpendData)
```

* Element added to `mod_obj` : `Stable` 
* Access via: `mod_obj$Stable` (data.frame)


# Load all Data at once

You can load all of the data in one step using `Load_Data` which takes the  `mod_obj` and a list with the file paths.
This function is a wrapper around the four functions described above. If only a subset of paths is supplied, the data for which the paths are given will be loaded, and a warning will be thrown indicating which data was not loaded.

```{r, error=TRUE,  eval=FALSE}
input_files = list(
  input_file_ModelData,
  input_file_FMIData,
  input_file_SpendData,
  input_file_MSRPData
)

mod_obj <- Load_Data(mod_obj, input_files)
```

* Element added to `mod_obj` : `input_data`, `Stable`, `Ftable`, `Mtable`
* Access via: (see above).
